---
title: "House Rent Prediction in Brazil"
author: "L. Hsieh, A. Monney, B. Remy, C. Steffe, R. Tombola"
date: "31 May, 2021"
output: 
  ioslides_presentation:
   widescreen: TRUE
   transition: "faster"
   logo: logo.png 
---

<style>
div.footnotes {
  position: absolute;
  left: 160px;
  margin-bottom: 5px;
  width: 80%;
  font-size: 0.6em;
}
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>
<script>
$(document).ready(function() {
  $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

  $('footnote').each(function(index) {
    var text  = $(this).html();
    var fnNum = (index+1).toString();
    $(this).html(fnNum.sup());

    var footnote   = fnNum + '. ' + text + '<br/>';
    var oldContent = $(this).parents('slide').children('div.footnotes').html();
    var newContent = oldContent + footnote;
    $(this).parents('slide').children('div.footnotes').html(newContent);
  });
});
</script>

```{r setup, include=FALSE}
source(here::here("scripts/setup.R"))
data <- read.csv(file = here::here("Data/data.csv")) #load previously cleand file from data part
```


## **Agenda** {.flexbox .vcenter}

- Point 1 
- Point 2
- Point 3

# Introduction {data-background=rio_couché.jpg data-background-size=cover}


# {data-background=data_presentation.PNG data-background-size=cover}

# {data-background=model_comparaison.PNG data-background-size=cover}


## **Regression Tree** {.flexbox .vcenter}

```{r echo=FALSE,  out.height="100%", out.width= "100%", warning = FALSE}
set.seed(2)
#model with kfol 10 and tuning parameter of k
knn.reg<-train(rent~.,data=df.tr,method = 'knn',trControl=trctrl,preProcess = c("center","scale"),tuneLength = 10)

knn.reg
```

